\chapter{Frontend Structure}


\section{Home Page}


\section{Visualization}


\section{GeoDB-Editor}


\section{Annotator}
\label{sec:annotator}


\section{Place URI List}


\section{Reporting}
\label{sec:reporting}


\section{Other Pages}


\subsection{Documents}

The documents page contains links to a few smaller pages and utilities.
Some of these are not available to all users, but only to developers or administrators.
Besides the page links listed in the following, the documents page also has links to the report creation page and the list of existing reports detailed in \cref{sec:reporting}.

\paragraph*{Database edit log.}
This page is visible only to administrators (role \verb!admin!).
It details the contents of the \verb!user_action! table in reverse chronological format.
This data can be reviewed for provenance, or to quickly retrieve an old value from a database entry after a mistake in an edit.

\paragraph*{REST API documentation.}
This page is visible to all developers (role \verb!dev!), and contains a list of the endpoints in the REST API (see~\cref{sec:rest-api}).
They are the HTTP endpoints under \verb!/rest/!, which are listed in the form they are defined in Flask.
The URL and possible HTTP verbs are extracted from Flask runtime information, and the documentation string is taken directly from the Python \emph{docstring} of that method.
The REST API methods' docstring are all quite detailed and show request and response content types, possible values and data entries, and payload or response examples, where applicable.

\paragraph*{Annotator user guide.}
The annotator user guide explains how the annotator works and is used in great detail\todo{Extract the guide and images into the Annotator section of this document.}, and with example images.
This page is visible to all users with the \verb!annotator! role.

\paragraph*{PostgreSQL Database Schema.}
Download link to a PDF of the database structure.
This link is available to all developers (role \verb!dev!) and to users with the \verb!pgadmin! role.
The PDF is the same as \cref{fig:db-structure}, enclosed in a page with headers and footers.

\paragraph*{Download database dump.}
Download link to a SQL dump of the entire database.
The file is served as GZIP-ed SQL, and is generated on the fly.
This functionality is available to all users.
However, if the requesting user does \emph{not} have the \verb!admin! role, the dump is data-only, and also omits the \verb!action_type!, \verb!user!, and \verb!user_action! provenance tables described in \cref{sec:provenance-tables}.


\subsection{DSGVO, Impressum, Cookie Preferences}


\subsection{Password Management}
